Supplementary material to: Drug efficacy prediction in cell lines

### 2019-02-19 docs/manuscript.Rnw
changed R code chuck options manuscript.Rnw and supplement.Rnw

@@

\begin{document}
	\maketitle

@@

	- drugs information: molecular target, drug class, etc (ask Oslo).

>>>>

% load packages
<<packages, include=FALSE, echo=FALSE>>=
library(cambridge)
@

% set options
<<settings, include=FALSE, echo=FALSE>>=
opts_knit$set(root.dir="..", base.dir="../figs")
opts_chunk$set(fig.align='center', fig.path="../figs/", 
               echo=FALSE, cache=FALSE, message=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("code/figures.R")
@

@@

\begin{document}

	\maketitle

@@

	- drugs information: molecular target, drug class, etc (ask Oslo), pubchem, omnipath DB, pharmaco DB

### 2019-02-19 docs/supplement.Rnw
changed R code chuck options manuscript.Rnw and supplement.Rnw

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,bbm,algorithm,algpseudocode,pgfplotstable,threeparttable, booktabs,mathtools,dsfont,parskip}

@@

% load packages and set options
<<settings, include=FALSE, echo=FALSE>>=
library(cambridge)
opts_knit$set(base.dir="../figs")
opts_chunk$set(fig.align='center', echo=FALSE, fig.path="../figs/", cache=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("../code/figures.R")
@

>>>>

% load packages
<<packages, include=FALSE, echo=FALSE>>=
library(cambridge)
@

% set options
<<settings, include=FALSE, echo=FALSE>>=
opts_knit$set(root.dir="..", base.dir="../figs")
opts_chunk$set(fig.align='center', fig.path="../figs/", 
               echo=FALSE, cache=FALSE, message=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("code/figures.R")
@

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,
rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,
bbm,algorithm,algpseudocode,pgfplotstable,threeparttable,booktabs,mathtools,
dsfont,parskip}

@@
